---
title: "Adelaide Crime Analysis Report_Wenchit"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
devtools::install_github("wenchi0922/hw2wenchit")
```

## Aim
The aim for this project is to compare the crime in the neighborhood: GOODWOOD and WAYVILLE according to the gathered statistic data from 2012~2017, expecifically in "Offence against person" .

## Results

The following is a example of the stastistic file from 2012~2013
```{r, results='asis'}
library(data.table)
library(readxl)
crime_data1 <- setDT(read_excel("../data/crime-statistics-2012-13.xlsx"))
knitr::kable(crime_data1)
```

Graph: 

```{r pressure, echo=FALSE}
library(hw2wenchit)
library(data.table)
library(ggplot2)
library(readxl)

filenames <- list.files("../data")
print(filenames)

crime_idx <- grep("crime-statistics", filenames)
print(crime_idx) 

crime_data <- filenames[crime_idx]
print(crime_data)

for (f in crime_data) {
  
adl_crime_suburb3(crime_data, "OFFENCES AGAINST THE PERSON" ,suburbs <- c("WAYVILLE", "GOODWOOD"))
  
}

```

## Discussion
(Plot not displaying porperly, not sure why) 
As the plot shows in the past couple years, the crime records in GOODWOOD is than WAYVILLE. Judging from this result, we can say that GOODWOOD is pissibly a more neignbrohood that WAYVILLE.
